Genome-wide changes in expression during inflorescence architecture development

### 2015-08-06 ms.Rmd
minor change to MS

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("cairo_pdf", "svg", "png"),
               fig.width=6.614,
               fig.height=6.614,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=TRUE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

tableCat <- function(inFrame){
	outText <- paste(names(inFrame), collapse=" | ")
	outText <- c(outText, paste(rep("---", ncol(inFrame)), collapse=" | "))
	invisible(apply(inFrame, 1, function(inRow){
		outText <<- c(outText, paste(inRow, collapse=" | "))
	}))
	return(outText)
}
```

@@

@@

To recover common expression patterns in the meristem samples, read counts were transformed using the variance-stabilizing transformation (VST) included in the `DESeq2` package [@Love:2014do], and the standardised, VST-transformed read counts were clustered using the fuzzy *c*-means algorithm implemented in the `Mfuzz` package [@Futschik:2005vo]. To determine the number of cluster cores (*c*), the minimum distance between cluster centroids, the formation of empty clusters, and PCA plots of cluster members were monitored for clusters produced with *c* values between `cmin` and `cmax` (@SI). A cluster number of `{r} c` was chosen (**`r I(pasteLabel("Figure", figCount, "f_mfuzzClusters"))`**).

<a id="f_mfuzzClusters"></a>
```{r f_mfuzzClusters, fig.cap="Fuzzy \\emph{c}-means clustering of normalised, transformed read counts"}
print(f_mfuzzClusters)
```

@@

>>>>

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("cairo_pdf"),
               fig.width=6.614,
               fig.height=6.614,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=TRUE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

tableCat <- function(inFrame){
	outText <- paste(names(inFrame), collapse=" | ")
	outText <- c(outText, paste(rep("---", ncol(inFrame)), collapse=" | "))
	invisible(apply(inFrame, 1, function(inRow){
		outText <<- c(outText, paste(inRow, collapse=" | "))
	}))
	return(outText)
}

capwords <- function(s, strict = FALSE) {
    cap <- function(s) paste(toupper(substring(s, 1, 1)),
                  {s <- substring(s, 2); if(strict) tolower(s) else s},
                             sep = "", collapse = " " )
    sapply(strsplit(s, split = " "), cap, USE.NAMES = !is.null(names(s)))
}

```

@@

# number of clusters (for text)
c <- length(unique(c1$cluster))

@@

To recover common expression patterns in the meristem samples, read counts were transformed using the variance-stabilizing transformation (VST) included in the `DESeq2` package [@Love:2014do], and the standardised, VST-transformed read counts were clustered using the fuzzy *c*-means algorithm implemented in the `Mfuzz` package [@Futschik:2005vo]. To determine the number of cluster cores (*c*), the minimum distance between cluster centroids, the formation of empty clusters, and PCA plots of cluster members were monitored for clusters produced with *c* values between `cmin` and `cmax` (@SI). A cluster number of `r as.character(english::english(c))` *justify chosing this? double diffential was closest to zero?* (**`r I(pasteLabel("Figure", figCount, "f_mfuzzClusters"))`**).

<a id="f_mfuzzClusters"></a>
```{r f_mfuzzClusters, fig.height=4.40933}
print(f_mfuzzClusters)
```

@@

`r I(pasteLabel("Figure", figCount, "f_mfuzzClusters"))`
**Fuzzy *c*-means clustering of normalised, transformed read counts**

`r capwords(as.character(english::english(c)))` common patterns of expression were recovered from the normalised, variance-stabilised read counts. Genes expressed in blah blah
